Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-19 manuscript-figures.Rmd
clean up figures; revert CT HPD data

MosqThermTraits_plot <- MosqThermTraits_df %>%
  # Set up plotting variables and theme
  # x = Temperature, y = trait value
  ggplot(mapping = aes(x = Temperature, y = value, group = system_ID)) +
  # Plot trait values:
  geom_line(aes(colour = system_ID), size = 1) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(10, 40),
    # breaks = seq(10, 40, 2)
  ) +
  # y-axis:
  scale_y_continuous(expand = c(0.05, 0)) +
  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  ) +
  # faceting:
  facet_wrap(~variable,
             nrow = 3, scales = "free",
             labeller = labeller(variable = label_parsed)
  ) +
  # legend:
  guides(color = guide_legend(override.aes = list(size = 4))) +
  # theme options:
  theme_minimal_vgrid(10) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(),
    legend.text = ggtext::element_markdown(),
    legend.direction = "vertical",
    legend.justification = "center",
    axis.title.x = element_text(hjust = 0),
    strip.text = element_text(
      face = "bold",
      hjust = 0
    )
  )

@@

infinite_skew <- 4500 # 10000

Topt_df <- Topt_df %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
                               sigmaH,
                               infinite_skew))
Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)

>>>>

MosqThermTraits_plot <- MosqThermTraits_df %>%
  # Set up plotting variables and theme
  # x = Temperature, y = trait value
  ggplot(mapping = aes(x = Temperature, y = value, group = system_ID)) +
  # Plot trait values:
  geom_line(aes(colour = system_ID), size = 1) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(10, 40),
    breaks = seq(10, 40, 2)
  ) +
  # y-axis:
  scale_y_continuous(expand = c(0.05, 0)) +
  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  ) +
  # faceting:
  facet_wrap(~variable,
             nrow = 3, scales = "free",
             labeller = labeller(variable = label_parsed)
  ) +
  # legend:
  guides(color = guide_legend(override.aes = list(size = 4))) +
  # theme options:
  theme_minimal_vgrid(10) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(),
    legend.text = ggtext::element_markdown(),
    legend.direction = "vertical",
    legend.justification = "center",
    axis.title.x = element_text(hjust = 0),
    strip.text = element_text(
      face = "bold",
      hjust = 0
    )
  )

@@

infinite_skew <- 10^3.7
# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^3.35 # 10^log10(max_sigmaH*1)

Topt_df <- data.Topt %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
                               sigmaH,
                               infinite_skew))
Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
